\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-12 experience.tex
Small change.
updated fabric figure to same style
Explain the use of generic and bug-specific test cases for MigratingTable in the evaluation section.
Also, better address the merits of generic and specific test cases in
the experience section, and associated clarifications.

\subsubsection{Input generation}

Of course, there are many possible input histories to test.  Since we originally hoped for a comprehensive form of verification and we didn't feel we had good intuition to prepare a set of specific test cases that would make us confident of having caught any and all concurrency bugs in the protocol, it was natural for us to sample from a distribution of input histories that we defined to exercise all the features of IChainTable2 within certain bounds.  Furthermore, it was natural to let \psharp control the choice of input history as well as the machine interleaving so we could reproduce both using a single random seed.

@@

% N.B. SpecTable = InMemoryTableWithHistory in the current codebase. ~ Matt 2015-08-17
To comprehensively verify the behavior of MigratingTable under an arbitrary input history, we needed some formulation of the IChainTable2 specification to which to compare it.  Since the specification is deterministic under sequential calls except for the results of streaming reads, we decided the easiest approach was to write an in-memory reference implementation called SpecTable.  Given a streaming read call, SpecTable can produce a set of all results that are compliant with the specification.  Our correctness property is then:
% Convert to some theorem-like environment? ~ Matt
\begin{quote}
For every execution trace of a collection of MigratingTables backed by the same pair of \term{old} and \term{new} SpecTables (where \psharp chooses the actual result of each streaming read from the valid set) in parallel with the migrator job, there exists a linearization of the combined input history such that the output in the original trace matches the output of a ``reference'' SpecTable on the linearized input.
\end{quote}
%
We instrumented MigratingTable to report the intended \term{linearization point} of each input call, which in our setting is always one of the corresponding \term{backend calls} to the backend tables (often the last).  Specifically, after each backend call completes, MigratingTable reports whether that call was the linearization point, which may depend on the result of the call.  This makes it possible to verify the correctness property as the model executes.  The model consists of a \psharp \term{tables machine} containing all three SpecTables; a collection of \term{service machines} containing identically configured MigratingTables; and a \term{migrator machine} that performs the background migration (Figure~\ref{fig:mockedmigration}).  Each service machine issues a random sequence of input calls to its MigratingTable, which sends backend calls to the tables machine.  When MigratingTable reports the linearization point of an input call, the service machine sends that input call to the reference table.  When an input call completes, the service machine checks that the results from the MigratingTable and the reference table agree.  \psharp controls the interleaving of the backend calls.  To ensure that the reference table is never observed to be out of sync with the backend tables, after the tables machine processes a backend call, it enters a state that defers further backend calls until MigratingTable has reported whether the backend call was a linearization point and (if so) the call to the reference table has been made.  We use the \psharp random scheduling strategy; we were afraid that an exhaustive strategy would only be feasible within bounds so low that we would miss some bugs.

@@

\begin{figure}[thb]
\centering
\includegraphics[width=\linewidth, clip=true, trim=0 180px 440px 0]{img/FabricModelOverview}
\caption{Overview of the key machines (rounded boxes) and interfaces (boxes) in our Fabric model.}
\label{fig:fabric_model}
\end{figure}

>>>>

\subsubsection{Input generation}
\label{sec:mtable:input}

% N.B. SpecTable = InMemoryTableWithHistory in the current codebase. ~ Matt 2015-08-17
Of course, there are many possible input histories for MigratingTable.  We could have tested specific input histories, but we were not confident that this approach would be effective in catching bugs, especially because concurrency increases the potential for interactions between different parts of the code that would be difficult for us to foresee.  If we had no formalization of the specification and had to rely on expected outputs worked out by hand, this might be the best we could do.  However, since the IChainTable2 specification is relatively simple and is almost deterministic under sequential calls, it was straightforward to write an in-memory reference implementation called SpecTable to which we can compare the output of MigratingTable on an arbitrary input history.  This gave us the attractive option to sample from a distribution we defined over all possible input histories within certain bounds.  It was convenient to let \psharp control the choice of input history as well as the schedule so we could reproduce both using a single random seed.  Then, under the ``small scope hypothesis'' that any bug in MigratingTable leads to incorrect output for at least one input history in our distribution, we have a positive probability of detecting this incorrect output on each iteration of the \psharp test.

@@

As mentioned above, the IChainTable2 specification is almost deterministic under sequential calls; the only nondeterminism is in the results of streaming reads.  Given a streaming read, SpecTable can compute the set of all results that are compliant with the specification, so we can simply check if the result of MigratingTable is in this set.  To test MigratingTable, we must supply it with backing tables.  We use SpecTable for this purpose as well, with \psharp choosing the actual result of each streaming read from the valid set.  Our correctness property is then:
% Convert to some theorem-like environment? ~ Matt
\begin{quote}
For every execution trace of a collection of MigratingTables backed by the same pair of \term{old} and \term{new} SpecTables in parallel with the migrator job, there exists a linearization of the combined input history such that the output in the original trace matches the output of a ``reference'' SpecTable on the linearized input.
\end{quote}
%
We instrumented MigratingTable to report the intended \term{linearization point} of each input call, which in our setting is always one of the corresponding \term{backend calls} to the backend tables (often the last).  Specifically, after each backend call completes, MigratingTable reports whether that call was the linearization point, which may depend on the result of the call.  This makes it possible to verify the correctness property as the model executes.  The model consists of a \psharp \term{tables machine} containing all three SpecTables; a collection of \term{service machines} containing identically configured MigratingTables; and a \term{migrator machine} that performs the background migration (Figure~\ref{fig:mockedmigration}).  Each service machine issues a random sequence of input calls to its MigratingTable, which sends backend calls to the tables machine.  When MigratingTable reports the linearization point of an input call, the service machine sends that input call to the reference table.  When an input call completes, the service machine checks that the results from the MigratingTable and the reference table agree.  \psharp controls the interleaving of the backend calls.  To ensure that the reference table is never observed to be out of sync with the backend tables, after the tables machine processes a backend call, it enters a state that defers further backend calls until MigratingTable has reported whether the backend call was a linearization point and (if so) the call to the reference table has been made.  We use the \psharp random scheduling strategy; we were afraid that an exhaustive strategy would only be feasible within bounds so low that we would miss some bugs.

@@

\begin{figure}[thb]
\centering
\includegraphics[width=\linewidth]{img/fabricmodel}
\caption{Overview of the key machines (rounded boxes) and interfaces (boxes) in our Fabric model.}
\label{fig:fabric_model}
\end{figure}
